---
title: "simulate"
output: html_document
date: '2022-02-20'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pacman::p_load(tidyverse, tsibble, fable, feasts, janitor, lubridate, tseries, TTR, xts, tsbox, quantmod, gridExtra)
```

```{r, message=FALSE}
assets <- read_csv("assets.csv") %>% 
    select(date, bitcoin, rsi_btc, mean_rsi_btc, sd_rsi_btc, score_btc, gold, rsi_gold, mean_rsi_gold, sd_rsi_gold, score_gold) %>% 
    mutate(date = mdy(date))
```

```{r}
convert <- function(from, to, from_amt, on_hand, curr_val) {
    if (str_detect(str_to_lower(from), "btc|bitcoin")) {
        #Converting from Bitcoin
        if (str_detect(str_to_lower(to), "usd|cash")) {
            #Bitcoin to cash
            if(from_amt > on_hand) {    #Check we have enough money for the conversion
                stop("'from_amount' is more than on hand amount")
            }
            conv = (from_amt * curr_val) * 0.98 #Calculate conversion
            
            res = tribble(
                ~amt, ~on_hand,
                conv, on_hand - from_amt
            )
            
            return(res) #return the conversion and the amount of currency left over
            
        } else {
            stop("Conversion type 'to' is invalid")
        }
    } else if (str_detect(str_to_lower(from), "gold")) {
        #Converting from gold
        if (str_detect(str_to_lower(to), "usd|cash")) {
            #Gold to cash
            if(from_amt > on_hand) {    #Check we have enough money for the conversion
                stop("'from_amount' is more than on hand amount")
            }
            conv = (from_amt * curr_val) * 0.99 #Calculate conversion
            
             res = tribble(
                ~amt, ~on_hand,
                conv, on_hand - from_amt
            )
            
            return(res) #return the conversion and the amount of currency left over left over
            
        } else {
            stop("Conversion type 'to' is invalid")
        }
    } else if (str_detect(str_to_lower(from), "usd|cash")) {
        #Converting from USD
        if (str_detect(str_to_lower(to), "btc|bitcoin")) {
            #USD to bitcoin
            if(from_amt > on_hand) {    #Check we have enough money for the conversion
                stop("'from_amount' is more than on hand amount")
            }
            conv = (from_amt / curr_val) * 0.98 #Calculate conversion
            
             res = tribble(
                ~amt, ~on_hand,
                conv, on_hand - from_amt
            )
            
            return(res) #return the conversion and the amount of currency left over
            
        } else if (str_detect(str_to_lower(to), "gold")) {
            #USD to gold
            if(from_amt > on_hand) {    #Check we have enough money for the conversion
                stop("'from_amount' is more than on hand amount")
            }
            conv = (from_amt / curr_val) * 0.99 #Calculate conversion
            
             res = tribble(
                ~amt, ~on_hand,
                conv, on_hand - from_amt
            )
            
            return(res) #return the conversion and the amount of currency left over
        } else {
            stop("Conversion type 'to' is invalid")
        }
    } else {
        stop("Conversion type 'from' is invalid")
    }
}
```

```{r}
test <- convert("btc", "usd", 10, 100, 500)
test$amt
test$on_hand

```


```{r}
get_curr_val <- function(df_row, from) {
    if (str_detect(str_to_lower(to), "btc|bitcoin")) {
        return(df_row$bitcoin)
    }
    else if (str_detect(str_to_lower(to), "gold")) {
        return(df_row$gold)
    } else {stop("Invalid 'from' type")}
}
```

```{r}
convert_no_trans <- function(from, to, from_amt, on_hand, curr_val) {
    if (str_detect(str_to_lower(from), "btc|bitcoin")) {
        #Converting from Bitcoin
        if (str_detect(str_to_lower(to), "usd|cash")) {
            #Bitcoin to cash
            if(from_amt > on_hand) {    #Check we have enough money for the conversion
                stop("'from_amount' is more than on hand amount")
            }
            conv = (from_amt * curr_val) #Calculate conversion
            
            res = tribble(
                ~amt, ~on_hand,
                conv, on_hand - from_amt
            )
            
            return(res) #return the conversion and the amount of currency left over
            
        } else {
            stop("Conversion type 'to' is invalid")
        }
    } else if (str_detect(str_to_lower(from), "gold")) {
        #Converting from gold
        if (str_detect(str_to_lower(to), "usd|cash")) {
            #Gold to cash
            if(from_amt > on_hand) {    #Check we have enough money for the conversion
                stop("'from_amount' is more than on hand amount")
            }
            conv = (from_amt * curr_val) #Calculate conversion
            
             res = tribble(
                ~amt, ~on_hand,
                conv, on_hand - from_amt
            )
            
            return(res) #return the conversion and the amount of currency left over left over
            
        } else {
            stop("Conversion type 'to' is invalid")
        }
    } else if (str_detect(str_to_lower(from), "usd|cash")) {
        #Converting from USD
        if (str_detect(str_to_lower(to), "btc|bitcoin")) {
            #USD to bitcoin
            if(from_amt > on_hand) {    #Check we have enough money for the conversion
                stop("'from_amount' is more than on hand amount")
            }
            conv = (from_amt / curr_val) #Calculate conversion
            
             res = tribble(
                ~amt, ~on_hand,
                conv, on_hand - from_amt
            )
            
            return(res) #return the conversion and the amount of currency left over
            
        } else if (str_detect(str_to_lower(to), "gold")) {
            #USD to gold
            if(from_amt > on_hand) {    #Check we have enough money for the conversion
                stop("'from_amount' is more than on hand amount")
            }
            conv = (from_amt / curr_val) #Calculate conversion
            
             res = tribble(
                ~amt, ~on_hand,
                conv, on_hand - from_amt
            )
            
            return(res) #return the conversion and the amount of currency left over
        } else {
            stop("Conversion type 'to' is invalid")
        }
    } else {
        stop("Conversion type 'from' is invalid")
    }
}
```

```{r}
sum_account <- function(account_table, btc_price, gold_price) {
    return(
        account_table[-1, "cash"] + 
        convert_no_trans("btc", "usd", account_table[-1, "bitcoin"], account_table[-1, "bitcoin"], btc_price) +
        convert_no_trans("gold", "usd", account_table[-1, "gold"], account_table[-1, "gold"], gold_price)
    )
}
```

if (score_bit >0 & score_gold> 0 ) {
    ratio <- score_bit/score_gold
    total_value <- ratiobitcoin + (1/ratio)(gold)
else if score_bit > 0 & score_gold < 0
    total_value <- score_btc*bitcoin + currancy
else if score_bit <0 & score_gold > 0 
    total_value <- score_gold*gold _ currancy
else 
    total_value <- lag(total_value)
}


```{r}
choose_currency <- function(x, account_table) {
    #x is just a dataframe with only 1 row, col_names are same as piped in df
    #account_table is the new table storing currency amounts
    
    # Ex: assets %>% head(5) %>% rowwise() %>% choose_currency()
        # where choose_currency() has "print(x$bitcoin)" will result in:
        # [1] 621.65 609.67 610.92 608.82 610.38
    
    # 1) Put however you decide currency and amount right here
    if(x$score_btc > 0 & x$score_gold > 0) {
        ratio <- x$score_btc/x$score_gold
        
        if(ratio > 1) {
           keep_gold <- (1/ratio) * account_table[-1, "gold"]
           sell_amt <- account_table[-1, "gold"] - keep_gold
           gold_in_usd <- convert("gold", "usd", sell_amt, account_table[-1, "gold"], get_curr_val(x, "gold"))
           
           #turn amt of gold into btc
           gold_in_btc <- convert("usd", "btc", gold_in_usd$amt, account_table[-1, "cash"], get_curr_val(x, "btc"))
           
           #Add to ledger
           account_table <- account_table %>% 
               add_row(cash = account_table[-1, "cash"],
                       bitcoin = gold_in_btc$amt + account_table[-1, "bitcoin"],
                       gold = keep_gold)
        }
        
        else if(ratio < 1) {
           keep_btc <- (1/ratio) * account_table[-1, "bitcoin"]
           sell_amt <- account_table[-1, "bitcoin"] - keep_btc
           btc_in_usd <- convert("btc", "usd", sell_amt, account_table[-1, "bitcoin"], get_curr_val(x, "bitcoin"))
           
           #turn amt of bitcoin into gold
           btc_in_gold <- convert("usd", "gold", btc_in_usd$amt, account_table[-1, "cash"], get_curr_val(x, "gold"))
           
           #Add to ledger
           account_table <- account_table %>% 
               add_row(cash = account_table[-1, "cash"],
                       bitcoin = keep_btc,
                       gold = btc_in_gold$amt + account_table[-1, "gold"])
            
        } else {
            # Just hold for the day
            account_table <- account_table %>% 
               add_row(cash = account_table[-1, "cash"],
                       bitcoin = account_table[-1, "bitcoin"],
                       gold = account_table[-1, "gold"])
        }

            
    } 
    else if(x$score_btc > 0 & x$score_gold < 0) {
        if(account_table[-1, "gold"] <= 100) {
            # Just hold for the day
            account_table <- account_table %>% 
               add_row(cash = account_table[-1, "cash"],
                       bitcoin = account_table[-1, "bitcoin"],
                       gold = account_table[-1, "gold"])
        } else {
            #Turn all gold except 100 into USD
            gold_to_usd <- convert("gold", "usd", account_table[-1, "gold"] - 100, account_table[-1, "gold"], get_curr_val(x, "gold"))
            
            if(score_btc < 1) {
                
                buy_amt <- (score_btc)*account_table[-1, "bitcoin"]
                buy_amt_usd <- convert("btc", "usd", buy_amt, account_table[-1, "bitcoin"], get_curr_val(x, "btc"))
                #Amount of btc we want to buy in cash
                buy_amt_usd <- min(buy_amt_usd$amt, account_table[-1, "cash"])
                
                #Convert it back to btc w/o transaction cost and append to ledger
                buy_amt <- convert_no_trans("usd", "btc", buy_amt_usd, account_table[-1, "cash"], get_curr_val(x, "btc"))
                
                account_table <- account_table %>% 
                   add_row(cash = account_table[-1, "cash"] - buy_amt_usd,
                           bitcoin = account_table[-1, "bitcoin"]+buy_amt$amt,
                           gold = account_table[-1, "gold"])
            } else if(score >= 1) {
                #Turn all cash into bitcoin
                btc_amt <- convert("usd", "btc", account_table[-1, "cash"], account_table[-1, "cash"], get_curr_val(x, "btc"))
                
                #Append to ledger
                account_table <- account_table %>% 
                   add_row(cash = account_table[-1, "cash"] - btc_amt$on_hand,
                           bitcoin = account_table[-1, "bitcoin"]+btc_amt$amt,
                           gold = account_table[-1, "gold"])
            }
        }
        
    } 
    else if(x$score_bit < 0 & x$score_bitcoin > 0) {
        if(account_table[-1, "bitcoin"] <= 100) {
            # Just hold for the day
            account_table <- account_table %>% 
               add_row(cash = account_table[-1, "cash"],
                       bitcoin = account_table[-1, "bitcoin"],
                       gold = account_table[-1, "gold"])
        } else {
            #Turn all gold except 100 into USD
            btc_to_usd <- convert("btc", "usd", account_table[-1, "bitcoin"] - 100, account_table[-1, "bitcoin"], get_curr_val(x, "bitcoin"))
            
            if(score_gold < 1) {
                
                buy_amt <- (score_gold)*account_table[-1, "gold"]
                buy_amt_usd <- convert("gold", "usd", buy_amt, account_table[-1, "gold"], get_curr_val(x, "gold"))
                #Amount of gold we want to buy in cash
                buy_amt_usd <- min(buy_amt_usd$amt, account_table[-1, "cash"])
                
                #Convert it back to gold w/o transaction cost and append to ledger
                buy_amt <- convert_no_trans("usd", "gold", buy_amt_usd, account_table[-1, "cash"], get_curr_val(x, "gold"))
                
                account_table <- account_table %>% 
                   add_row(cash = account_table[-1, "cash"] - buy_amt_usd,
                           bitcoin = account_table[-1, "bitcoin"],
                           gold = account_table[-1, "gold"]+buy_amt$amt)
            } 
            else if(score >= 1) {
                #Turn all cash into gold
                gold_amt <- convert("usd", "gold", account_table[-1, "cash"], account_table[-1, "cash"], get_curr_val(x, "gold"))
                
                #Append to ledger
                account_table <- account_table %>% 
                   add_row(cash = account_table[-1, "cash"] - gold_amt$on_hand,
                           bitcoin = account_table[-1, "bitcoin"],
                           gold = account_table[-1, "gold"]+gold_amt$amt)
            }
        }
        
    } 
    else {
        if((account_table[-1, "bitcoin"] <= 100) | (account_table[-1, "gold"] <= 100)) {
            # Just hold for the day
            account_table <- account_table %>% 
               add_row(cash = account_table[-1, "cash"],
                       bitcoin = account_table[-1, "bitcoin"],
                       gold = account_table[-1, "gold"])
        }
        else {
            #Sell everything, put it all in USD
            btc_usd <- convert("btc", "usd", account_table[-1, "bitcoin"]-100, account_table[-1, "bitcoin"], get_curr_val(x, "btc"))
            gold_usd <- convert("gold", "usd", account_table[-1, "gold"]-100, account_table[-1, "gold"], get_curr_val(x, "gold"))
            
            #Append ledger
            account_table <- account_table %>% 
               add_row(cash = account_table[-1, "cash"] + btc_usd$amt + gold_usd$amt,
                       bitcoin = btc_usd$on_hand,
                       gold = gold_usd$on_hand)
        }
    }
}
```

```{r}
account_table <- tribble(
    ~cash, ~bitcoin, ~gold,
    1000, 0, 0,
    980.92, 0.01, 0.01
)

assets %>% head(5) %>% 
    rowwise() %>% 
    
```
```{r}
res = tribble(
    ~x, ~y, 
    1, 5, 
    4, 6
)

res[-1,'y']
```

